Estimating duration in the presence of misclassification

### 2024-01-30 transmission.tex
Start conclusion

The major contribution in this chapter is showing that transmission and incidence can be estimated using only a

>>>>

The major contribution in this chapter is showing that transmission and incidence can be estimated using only data from the CIS.
A similar survey could, therefore, be considered as the primary form of surveillance for a future pandemic.
The advantage of such a setup is the unbiased information across the entire population, including children.

The transmission model presented in this chapter could be extended to fully extract the information in the CIS (see \cref{SEIR:sec:discussion}).
This would require a more flexible model, which would likely require a more efficient inference procedure, such as NUTS.
